\documentclass{article}
\title{Orx Animation Editor Help}
\author{Enis Bayramoglu (enobayram)}
\date{\today}
\begin{document}
\maketitle
\tableofcontents

\section{Preface}
This help system is meant to fill the need for a minimal help support for the Orx Animation Editor. I reckon that as the editor complexity increases,
we'll probably end up using a more advanced help browser, but for now, I hope this will suffice.

I'm planning to update this document as new features are added, but if you notice that it's outdated, please inform me (enobayram) on the Orx forums.

\section{Introduction}
The Orx Animation Editor has been created with a hope to satisfy the need for \textbf{minimal} animation editing without touching Orx .ini files. As nice as
.ini files might be, they're a bit cumbersome for specifying sprite animations and animation sets. I imagine they must also be cumbersome for skeletal
animations, but they are, as of now, out of scope of this editor, since much more professional programs (like Spriter) are under development for that purpose. Unless the duplicated (and hard) work for skeletal animations is justified, I am planning to stick to the mentioned minimal scope.

Note that the Orx Animation Editor is heavily under development, and it's even hard to call it at its alpha stage. That said, I've already started using it for
my personal projects, and I hope it will be useful to someone even with its current set of features. If you start using it for any real purpose, and plan to invest
effort into it, please let me know at the \textit{Orx Animation Editor} thread in the Orx forums.

\section{Set Project Dialog}

\subsection{New Animation Project}

\subsection{Open Animation Project}

\section{Animation Manager}

\section{Animation Viewer}

\section{Frame Editor}

\section{Animation Set Editor}

\section{Menu Bar}

\subsection{File}

\subsection{Edit}

\subsection{Help}

\end{document}
